% ----------------------------------------------------------------------%
%	By Alessandro Plasmati (http://aleplasmati.comuv.com) - 05/27/2009	%
%	Modified by Sean Anderson (http://www.roguephysicist.org)			%
%	Licensed under the Creative Commons Attribution 3.0 Unported		%
%	Share, change, spread, and have fun!								%
%	http://creativecommons.org/licenses/by/3.0/							%
% ----------------------------------------------------------------------%

\documentclass[letterpaper,10pt]{article}
\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry}               
\usepackage{bbding}
\usepackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{fontspec}
\usepackage[absolute]{textpos}

%-----------------------------Fonts---------------------------------%
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Mapping=tex-text]{Linux Libertine O}		% http://www.linuxlibertine.org/
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Linux Biolinum O}	% http://www.linuxlibertine.org/
\setmonofont[Scale=MatchLowercase]{FreeMono}			% http://www.gnu.org/software/freefont/

%--------------------Link colors and pdf info-----------------------%
\usepackage{hyperref}
\definecolor{shade}{HTML}{CAE1FF}
\definecolor{headings}{HTML}{701112}
\definecolor{links}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=links,pdftitle=Sean M. Anderson - Curriculum Vitae (Abridged),pdfauthor=Sean M. Anderson}

%-----------------------------Watermark-----------------------------%
\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{4mm}{0.2\paperheight}
\setlength{\parindent}{0pt}

%----------------------Custom section headings----------------------%
\usepackage{titlesec}
\titleformat{\section}
{\color{headings}\scshape\sffamily\Large\raggedright}{}{0em}{}[\color{black}\titlerule]
\titlespacing{\section}{0pt}{0pt}{5pt}

\pagestyle{empty}

\begin{document}

% Watermark
\begin{textblock}{1}(0,-9.5)
\rotatebox{90}{\parbox{500mm}{\color{black}\sffamily Updated \today. {\href{http://www.roguephysicist.org}{\textsc{roguephysicist.org}}}}}
\end{textblock}

\centering
{\Huge \textsc{Sean M. Anderson}}\\	
{\Large\color{headings}\sffamily{Curriculum Vitæ}\\[20pt]}
	
\begin{minipage}[t]{0.5\textwidth} % Left column

	\vspace{0pt}	%trick for alignment
	
\section{Work Experience}
	\raggedleft
	\textsc{\normalsize Jan. 2007 -- Jun. 2009}\\
	\raggedright{\large Freelance Photographer\\
	\emph{Buenos Aires, AR}}\\[5pt]
	\normalsize{Execution of several projects, both personal and professional. Creation of several personal websites, and content for others.}\\[10pt]

	\raggedleft
	\textsc{\normalsize Summer 2006}\\
	\raggedright{\large Part-Time Faculty\\
	\emph{University of Alabama in Huntsville, US}}\\[5pt]
	\normalsize{Created and taught the first offering of Physics of Photography, PH489. This one credit course provided a fundamental overview of optics and image creation, in relation to photography. Offered to secondary education teachers for 3 days (intensive) during summer semester.}\\[10pt]

	\raggedleft
	\textsc{\normalsize Aug. 2005 -- Dec. 2006}\\
	\raggedright{\large Translation Consultant\\
	\emph{Parent Tutor Corporation, US}}\\[5pt]
	\normalsize{English to Spanish translation of Tutorials designed for parents with young children, grades kindergarten through 8th.}\\[10pt]

	\raggedleft
	\textsc{\normalsize Fall 2004 -- Fall 2005}\\
	\raggedright{\large Teaching Assistant\\
	\emph{University of Alabama in Huntsville, US}}\\[5pt]
	\normalsize{Instructed undergraduate Physics labs 2 and 3 corresponding to classes PH112 and PH113 respectively.}\\[10pt]

	\raggedleft
	\textsc{\normalsize Fall 2002 -- Summer 2006}\\
	\raggedright{\large Research/Technical Assistant\\
	\emph{University of Alabama in Huntsville, US}}\\[5pt]
	\normalsize{Research on a variety of topics including: sensors, applications of optical infrared transmitters and receivers for transmiting information from rotating platforms to stationary bases, thin film optical analysis and testing, transmittance and optical properties of helicopter fluids, testing of LED based anti-collision airplane lights, holography, and sonoluminescence.}\\[12pt]

\section{\textsc{Skills}}
	\begin{tabular}{rl}
		Expert			&	Computer Hardware, Image Manipulation, \LaTeX\\ 
		Intermediate	&	Linux, FOSS, HTML, CSS, Video Editing\\
		Beginner		&	Parallel Programming, Python, HPC
	\end{tabular}\\[12pt]

\section{Languages}
	\begin{tabular}{rl}
		\textsc{English}	&	Native Language\\
		\textsc{Spanish}	&	Fluent
	\end{tabular}

\end{minipage}
\hfill
\begin{minipage}[t]{0.44\textwidth} % Right column
	
	\vspace{0pt} %trick for alignment
	
\colorbox{shade}{\sffamily
\begin{tabular}{c|p{7cm}}
							& US Citizen, 28 Years Old\\
\raisebox{-3pt}{\Phone}		&+52 1 473 104 4835\\
\raisebox{-3pt}{\Envelope}	&\href{mailto:sma@roguephysicist.org}{sma@roguephysicist.org}
\end{tabular}}\\

\section{Education}
	\begin{tabular}{rl}
		\textsc{Jan.} 2012	&	Master of Science \textsc{(Optical Science)}\\
							&	\textbf{Centro de Investigaciones en Óptica}, MX\\
							&	Thesis: Optical Nonlinear Spectroscopy of\\
							&	\hspace{31pt}Gold and Silicon Nanoparticles\\
							&	\normalsize GPA: 9.49/10.0\\
							&	\\
	\textsc{May} 2006	&	Bachelor of Science in \textsc{Physics}\\
							&	with minor in \textsc{Mathematics}\\
							&	\small\emph{magna cum laude}\\
							&	\textbf{University of Alabama in Huntsville}, US\\
							&	\normalsize GPA: 9.675/10
	\end{tabular}\\

\section{Honors and Awards}
	\begin{tabular}{l l}
		Highest Master Student GPA					&	\textsc{Mar.} 2011\\
		Departmental Physics Honors					&	\textsc{May} 2006\\
		Barry Goldwater Foundation Nomination		&	2004, 2005\\
		Gerhard Heller Memorial Scholarship			&	2003 -- 2006\\
		Dean's List of Distinguished Students		&	2002 -- 2006\\
		Academic Excellence Scholarship				&	2002 -- 2006    
	\end{tabular}\\

\section{Publications}
	E. Hong, A. Krishnamurthy, D. Gregory, S. Anderson. Optical slip ring for sensor interface applications. 2006. \emph{Sensors for Propulsion Measurement Applications, SPIE Proceedings Volume 6222.}\\[5pt]
	D. Solís, T. López-Luke, E. De La Rosa, O. Meza, S. Anderson. Syntonized white up-converted emission by Tm$^{3+}$-Yb$^{3+}$-Er$^{3+}$-Ho$^{3+}$ doped ZrO$_{2}$ nanocrystals. 2010. \emph{Light-Emitting Diodes: Materials, Devices, and Applications for Solid State Lighting XIV, SPIE Proceedings Volume 7617.}\\[5pt]
	S. Corzo-Garcia, R. Medina-Lopez, S. Anderson, E. Castro-Camus, R. Carriles, A. Ruiz-Marquez. Reliable and economical method to join optical tables. 2011. \emph{Optics and Lasers in Engineering 49, 1251–1253.}\\

\section{Interests and Activities}
	\begin{tabular}{l|l|l}
		Open-Source	&	Cinema		&	Cooking\\
		Linux		&	Photography	&	Travel\\
		HPC			&	Tango		&	Adventure
	\end{tabular}
\end{minipage} 

\end{document}  
